Building Large-Scale Cross-lingual Knowledge Base from Multi-Wiki

### 2015-06-07 nlpcc/paper.tex
删了uri table

@@

\begin{document}
\begin{CJK*}{UTF8}{song}
\mainmatter

@@

\begin{table}[h]
\small
\centering
\caption{Statistics of elementary extraction result}
\label{tab:extract-result}
    \begin{tabular}{|l|l|l|l|l|}
        \hline
                   & Enwiki  & Zhwiki & Hudong  & Baidu   \\ \hline
        \#Instance & 4304113 & 662650 & 5590751 & 5622404 \\ \hline
        \#Class    & 982432  & 159705 & 31802   & 1300    \\ \hline
        \#Property & 43976   & 18842  & 1187    & 139634  \\ \hline
    \end{tabular}
\end{table}

@@

We create URIs to identify each element and provide corresponding information if users look up elements over HTTP protocol to achieve the knowledge base. Table \ref{tab:uris} lists the defined URIs.
\begin{table}[h]
\small
\centering
\caption{URIs for class, instance, property in our knowledge base}
\label{tab:uris}
    \begin{tabular}{|c|c|}
        \hline
        Type     & URI                     \\ \hline
        Class    & http://clkb/class/id    \\ \hline
        Instance & http://clkb/instance/id \\ \hline
        Property & http://clkb/property/id \\ \hline
    \end{tabular}
\end{table}

@@

\begin{figure}
    \centering
    \begin{minipage}[t]{0.8\textwidth}
        \centerline{\includegraphics[width=0.8\columnwidth]{fig/search-engine}}
        \caption{A Sample Query for Using Search Box }
        \label{fig:search-engine}
    \end{minipage}%
    \begin{minipage}[t]{0.8\textwidth}
        \centerline{\includegraphics[width=0.8\columnwidth]{fig/sparql-endpoint}}
        \caption{A SPARQL Sample Query over the Knowledge Base}
        \label{fig:sparql-endpoint}
    \end{minipage}%
\end{figure}

\section{Related Work}
\label{sec:work}
In this section, we introduce some related knowledge bases and cross-lingual knowledge linking methods.
\subsection{Chinese Knowledge Bases}
Currently, several large-scale Chinese knowledge bases have been generated. Zhishi.me\cite{niu2011zhishi,wang2014publishing} is the first published Chinese large-scale Linking Open Data. It acquires structural information from three original sources, Chinese Wikipedia, Baidu Baike and Hudong Baike and gains more than 5 million distinct entities. Zhishi.me helps generate knowledge base focused on relations in Junfeng Pan’s work\cite{pan2012building}.
Similar with Zhishi.me, CKB\cite{wang2012building} is created from Hudong Baike. It first learns an ontology based on category system and properties, and then collects 19542 classes, 2381 properties, 802593 instances. Besides using existing encyclopedias, CASIA-KB employs other types of sources(e.g. microblog posts, news pages, images) to enrich the structured knowledge.
\subsection{Cross-lingual Knowledge Bases}
DBpedia \cite{auer2007dbpedia,mendes2012dbpedia} is one of the most used cross-lingual knowledge base in the world. It extracts various kinds of structured information from Wikipedia and employ the multilingual characteristic of Wikipedia to generate 97 language versions of content. This knowledge base is widely applied in many domains, including media recommendation \cite{fernandez2011generic,kaminskas2012knowledge}, entity linking\cite{mendes2011evaluating} and information extraction \cite{dutta2013integrating}. Universal WordNet(UWN)\cite{de2012uwn} is a large multilingual lexical knowledge base which is build from WordNet and enriched its entities from Wikipedia. It is constructed using sophisticated knowledge extraction, link prediction, information integration, and taxonomy induction methods. The API is available to over 200 languages and more than 16 million words and names. UWN provides semantic relationship of list of word meanings for Aya's work on classual search \cite{al2015classual}

@@

\section{Conclusion}
\label{sec:con}
This paper presents a procedure of building a Chinese-English CLKB from four encyclopedia sources. At first, we extract structured information and unify data format. Then a cross-lingual language link set is generated and expanded to help combine the bilingual sources. To refine our dataset, we also conduct pruning work on taxonomy. Finally, we acquire a CLKB containing XXX classes, XXX instances and XXX properties. Currently, a website and SPARQL query interface is provided to access the knowledge base.

@@

\end{CJK*}
\end{document}

>>>>

\usepackage{xeCJK}
\setCJKmainfont[BoldFont=STHeiti, ItalicFont=STKaiti]{STSong}
\setCJKsansfont[BoldFont=STHeiti]
\setCJKmonofont{STFangsong}

%\usepackage[BoldFont,SlantFont,CJKchecksingle]{xeCJK}
%\setCJKmainfont[BoldFont=SimHei]{SimSun}
%\setCJKmonofont{SimSun}% 设置缺省中文字体
%\usepackage{CJKutf8}

@@

\begin{document}
%\begin{CJK*}{UTF8}{song}
\mainmatter

@@

\begin{table}[]
    \small
    \centering
    \caption{Statistics of elementary extraction result}
    \label{tab:extract-result}
        \begin{tabular}{|l|l|l|l|l|}
            \hline
                       & Enwiki  & Zhwiki & Hudong  & Baidu   \\ \hline
            \#Instance & 4304113 & 662650 & 5590751 & 5622404 \\ \hline
            \#Class    & 982432  & 159705 & 31802   & 1300    \\ \hline
            \#Property & 43976   & 18842  & 1187    & 139634  \\ \hline
        \end{tabular}
\end{table}

@@

We create URIs \uri{http://clkb/type/id} (type could be \textit{class}, \textit{instance}, \textit{property}) to identify each element and provide corresponding information if users look up elements over HTTP protocol to achieve the knowledge base.

@@

\begin{figure}
    \begin{minipage}[t]{0.5\textwidth}
        \centerline{\includegraphics[width=5.5cm,height=3cm]{fig/search-engine}}
        \caption{A picture of Search Box}
        \label{fig:search-engine}
    \end{minipage}%
    \begin{minipage}[t]{0.5\textwidth}
        \centerline{\includegraphics[width=5.5cm,height=3cm]{fig/sparql-endpoint}}
        \caption{A SPARQL Sample Query}
        \label{fig:sparql-endpoint}
    \end{minipage}%
\end{figure}

\section{Related Work}
\label{sec:work}
In this section, we introduce some related knowledge bases and cross-lingual knowledge linking methods.
\subsection{Chinese Knowledge Bases}
Currently, several large-scale Chinese knowledge bases have been generated. Zhishi.me\cite{niu2011zhishi,wang2014publishing} is the first published Chinese large-scale Linking Open Data. It acquires structural information from three original sources, Chinese Wikipedia, Baidu Baike and Hudong Baike and gains more than 5 million distinct entities. Zhishi.me helps generate knowledge base focused on relations in Junfeng Pan’s work\cite{pan2012building}.
Similar with Zhishi.me, CKB\cite{wang2012building} is created from Hudong Baike. It first learns an ontology based on category system and properties, and then collects 19,542 classes, 2,381 properties, 802,593 instances. Besides using existing encyclopedias, CASIA-KB employs other types of sources(e.g. microblog posts, news pages, images) to enrich the structured knowledge.
\subsection{Cross-lingual Knowledge Bases}
DBpedia \cite{auer2007dbpedia,mendes2012dbpedia} is one of the most used cross-lingual knowledge base in the world. It extracts various kinds of structured information from Wikipedia and employ the multilingual characteristic of Wikipedia to generate 97 language versions of content. This knowledge base is widely applied in many domains, including media recommendation \cite{fernandez2011generic,kaminskas2012knowledge}, entity linking\cite{mendes2011evaluating} and information extraction \cite{dutta2013integrating}. Universal WordNet(UWN)\cite{de2012uwn} is a large multilingual lexical knowledge base which is build from WordNet and enriched its entities from Wikipedia. It is constructed using sophisticated knowledge extraction, link prediction, information integration, and taxonomy induction methods. The API is available to over 200 languages and more than 16 million words and names. UWN provides semantic relationship of list of word meanings for Aya's work on classual search \cite{al2015classual}

@@

\section{Conclusion}
\label{sec:con}
This paper presents a procedure of building a Chinese-English CLKB from four encyclopedia sources. At first, we extract structured information and unify data format. Then a cross-lingual language link set is generated and expanded to help combine the bilingual sources. To refine our dataset, we also conduct pruning work on taxonomy. Finally, we acquire a CLKB containing 663,740 classes, 11,721,238 instances and 56,449 properties. Currently, a website and SPARQL query interface is provided to access the knowledge base.

@@

%\end{CJK*}
\end{document}
